---
title: "| RESEARCH PROTOCOL\n| \n| Systematic review of outcome misclassification correction in pharmacoepidemiology\n"
fontsize: 10pt
geometry: margin=1in
output:
  bookdown::html_document2:
    df_print: paged
    toc: yes
    toc_depth: 2
    toc_float: yes
    number_sections: yes
    number_tables: yes
    css: "style.css"
header-includes:
- \usepackage[numbers,sort&compress]{natbib}
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{caption}
- \usepackage{rotating}
- \usepackage{multirow}
- \usepackage{mwe,tikz}
- \usepackage[percent]{overpic}
- \usepackage{enumitem}
- \usepackage{hyperref}
- \newcolumntype{P}[1]{>{\raggedright\arraybackslash}p{#1}}
- \newcommand{\footerDate}{`r params$date`}
- \input{header.tex}
longtable: yes
mainfont: Arial
bibliography: Protocol.bib
params:
  date: '2021-10-26'
  version: 1.0
subtitle: 'Version: `r params$version`'
link-citations: true
csl: jamia.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(kableExtra.latex.load_packages = FALSE)
library(kableExtra)
library(dplyr)
options(knitr.kable.NA = "")
if (!knitr::is_latex_output() && !knitr::is_html_output()) {
  options(knitr.table.format = "simple")
}

pdf2png <- function(path) {
  # only do the conversion for non-LaTeX output
  if (knitr::is_latex_output()) {
    return(path)
  }
  path2 <- xfun::with_ext(path, "png")
  img <- magick::image_read_pdf(path)
  magick::image_write(img, path2, format = "png")
  path2
}

latex_table_font_size <- 8

#source("PrintCohortDefinitions.R")

#numberOfNcs <- nrow(readr::read_csv("../inst/settings/NegativeControls.csv", col_types = readr::cols()))

```

# List of Abbreviations

```{r abbreviations, echo=FALSE, results="asis", warning=FALSE}
abbreviations <- readr::read_delim(col_names = FALSE, delim = ";", trim_ws = TRUE, file = "
CI;Confidence interval
COVID-19;Coronavirus disease 2019
EHR;Electronic health record
HR;Hazard ratio
NPV;Negative predictive value
OR;Odds ratio
PPV;Positive predictive value
QBA;Quantitative bias analysis
RCT;Randomized-controlled clinical trial
RR;Relative risk
RWD;Real-world data
RWE;Real-world evidence
")

tab <- kable(abbreviations, col.names = NULL, linesep = "", booktabs = TRUE) %>%
  column_spec(1, width = "10em")

if (knitr::is_latex_output()) {
  tab %>% kable_styling(latex_options = "striped", font_size = latex_table_font_size)
} else {
  tab %>% kable_styling(bootstrap_options = "striped")
} 
```

# Investigators

```{r parties, echo=FALSE, results="asis", warning=FALSE}
parties <- readr::read_delim(col_names = TRUE, delim = ";", trim_ws = TRUE, file = "
  Investigator; Contact
  James Weaver ^1,2,3^ *;james.weaver@ndorms.ox.ac.uk
  Patrick B. Ryan ^2,3,4^;ryan@ohdsi.org
  Victoria Strauss ^1,2^;victoria.strauss@csm.ox.ac.uk
  Marc A. Suchard ^3,5^;msuchard@ucla.edu
  Daniel Prieto-Alhambra ^1,3,6^;daniel.prietoalhambra@ndorms.ox.ac.uk
")

tab <- kable(parties, booktabs = TRUE, linesep = "") %>% 
  column_spec(1, width = "20em") %>%
  #column_spec(2, width = "30em") %>%
  footnote(general = "* Principal Investigator", general_title = "") %>%
  footnote(general = "^1^ Centre for Statistics in Medicine, Nuffield Department of Orthopedics, Rheumatology and Musculoskeletal Sciences, Oxford University, Oxford, UK", general_title = "") %>%
  footnote(general = "^2^ 2Observational Health Data Analytics, Global Epidemiology, Janssen Research and Development, Titusville, NJ, USA", general_title = "") %>%
  footnote(general = "^3^ Observational Health Data Sciences and Informatics, New York, NY, USA", general_title = "") %>%
  footnote(general = "^4^ Department of Biomedical Informatics, Columbia University Medical Center, New York, NY, USA", general_title = "") %>%
  footnote(general = "^5^ Department of Biostatistics, Fielding School of Public Health, and Department of Biomathematics, David Geffen School of Medicine, UCLA, Los Angeles, CA, USA", general_title = "") %>%
  footnote(general = "^6^ Medical Informatics, Erasmus Medical Centre, Rotterdam, Netherlands", general_title = "")

if (knitr::is_latex_output()) {
  tab %>% kable_styling(latex_options = "striped", font_size = latex_table_font_size)
} else {
  tab %>% kable_styling(bootstrap_options = "striped")
}
```

## Disclosures

This study is undertaken within Observational Health Data Sciences and Informatics (OHDSI), an open science collaboration.
**JW** and **PR** are employees of shareholders of Janssen R&D (a Johnson & Johnson company).
**MAS** receives grant support from the US National Institutes of Health, US Food & Drug Administration and US Department of Veterans Affairs and contracts from Janssen R&D.
<mark>**VS**..</mark>.
**DPA**’s research group has received grant support from Amgen, Chesi-Taylor, Novartis, and UCB Biopharma. His department has received advisory, consultancy fees from Amgen, Astellas, AstraZeneca, Johnson & Johnson, and UCB Biopharma and fees for speaker services from Amgen and UCB Biopharma. Janssen, on behalf of IMI-funded EHDEN and EMIF consortiums, and Synapse Management Partners have supported training programmes organised by DPA's department and open for external participants organized by his department outside submitted work.

## Collaborators
Eli Harriss of Oxford Bodleian Libraries


# Review information

## Anticipated or actual start date

2021-11-01

## Anticipated completion date

2022-06-01

## Stage of review

```{r stages, echo=FALSE, results="asis", warning=FALSE}
stages <- readr::read_delim(col_names = TRUE, delim = ";", trim_ws = TRUE, file = "
  Review stage; Started; Completed
  Preliminary searches; Yes; No
  Piloting of the study selection process; No; No
  Formal screening of search results against eligibility criteria; No; No
  Data extraction; No; No
  Risk of bias (quality) assessment; No; No
  Data analysis; No; No
")

tab <- kable(stages, booktabs = TRUE, linesep = "") %>% 
  column_spec(1, width = "30em") %>%
  column_spec(2, width = "5em") %>%
  column_spec(3, width = "5em")

if (knitr::is_latex_output()) {
  tab %>% kable_styling(latex_options = "striped", font_size = latex_table_font_size)
} else {
  tab %>% kable_styling(bootstrap_options = "striped")
}
```

# Abstract

**Background**

Outcome misclassification is acknowledged but rarely corrected for in causal inference studies using observational data. Quantitative bias analysis (QBA) is a method for outcome misclassification correction, but it is unclear how often it is used and the extent to which it minimizes bias in effect estimates.

The existing literature generally reports study results from one exposure comparison, for one outcome, in one database, using one QBA type. Existing evaluations of QBA performance are subject to variability from different research questions, study designs, analytic implementations, and contexts where there is no a priori expectation about the true result. This review will inform whether novel QBA methodological research should be subsequently designed and executed using strictly consistent study design, analytic implementation, and applied to research questions where the estimates are expected to be null (i.e., negative control exposure-outcome pairs).

**Objectives**

* Characterize use of QBA for outcome misclassification correction in pharmacoepidemiologic literature
* Assess the impact QBA for outcome misclassification correction on effect measure estimates
* Explore QBA methodological variables that may explain impact 

**Search methods**

We searched <mark>X electronic databases</mark> from 2006-01-01 to <mark>YYYY-MM-DD. Sentence on validated search strategy here</mark>. We restricted to English language studies.

**Selection criteria**

We queried and examined clinical and methodological studies that used validation study results as QBA input to generate effect estimates corrected for outcome misclassification.

**Data collection and analysis**

The following outcome measures will be collected from included studies: relative risks or rate ratios (RR), odds ratios (OR), and hazard ratios (HR) point estimates and associated standard errors. The systematic review outcome measures are bias, mean squared error, and precision difference.

```{r child = "mainText.Rmd"}
```

# References {-}

<div id="refs"></div>